Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-18 ms.qmd
Map current

world_map = map_data("world")

ggplot() +
  geom_map(
    data = world_map, map = world_map,
    aes(long, lat, map_id = region),
    color = "black", fill = "lightgray") +
  geom_point(
    data = all_pred,
    aes(long.x, lat.y, color = Estimate),
    alpha = 0.7
  ) +
  theme_void() +
  theme(legend.position = "none")

>>>>

world_map = map_data("world") %>% 
  filter(! long > 180)

map1_current <- ggplot() +
  geom_map(
    data = world_map, map = world_map,
    aes(long, lat, map_id = region),
    color = "black", fill = "lightgray") +
  expand_limits(x = world_map$long, y = world_map$lat) +
  coord_map("moll") +
  geom_point(
    data = all_pred,
    aes(long.x, lat.y, color = Estimate),
    alpha = 0.7, size = 6
  ) + labs(x = "Longitude", y = "Latitude", color = TeX("$lnCVR_{Q_{10}}$")) +
   theme_map()
map1_current
